---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
library(ggplot2)
```

## The Binomial package simulates the binomial distribution and provides a way to visualize the distribution.
 
### The bin_choose function finds the number of combination for a given number of trials and successes, with successes vectorized

```{r}
bin_choose(successes=5, trials=7)
bin_choose(successes=1:5, trials=7)

```

### The binomial probability function finds the probability for a given number of successes given trials and probability. Succeses is vectorized.

```{r}
bin_probability(successes = 2, trials = 5L, prob = 0.5)

bin_probability(successes = 0:2, trials = 5L, prob = 0.5)
```

### The binomial distribution function finds the distribution of a given number of trials for a given probability. Along with a helpful plot method

```{r}
x <- bindis(trials = 5L, prob = 0.5)

plot(x)
```

### The binomial cumulative function finds the cumulative sum of the distribution at every success. It includes a plot method

```{r}
y <- bincum(trials = 5L, prob = 0.5)

plot(y)

```



