---
title: "README"
author: "John Friedman"
date: "4/29/2019"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

`"binomial"` is a [R](http://www.r-project.org/) package containing functions to simulate and graph the binomial distribution

* `bin_choose` returns combinations of successes and trials
* `bin_kurtosis` returns kurtosis given number of trials and probability
* `bin_mean` returns mean given number of trials and probability
* `bin_mode` returns mode given number of trials and probability
* `bin_skewness` returns skewness given number of trials and probability
* `bin_variance` returns variance given number of trials and probability
* `bin_probability` returns probability given number of successes,trials and  probability
* `binvar` creates an object of class Binomial variable
* `bindis` creates a data frame of successes by probability
* `plot.bindis` plots bindis objects
* `bincum` creates a data frame of successes summed over probability
* `plot.bincum` plots bincum objects




## Motivation

This package was made for the Class Stat 133 at UC Berkeley.


## Installation

Use `"devtools"` to install from github:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (no vignettes)
devtools::install_github("https://github.com/stat133-sp19/hw-stat133-jgoman99/tree/master/workout03")
# install "binomial" (has vignettes)
devtools::install_github("https://github.com/stat133-sp19/hw-stat133-jgoman99/tree/master/workout03", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)
library(ggplot2)
#bin choose
bin_choose(1,4)

#bin kurtosis
bin_kurtosis(3,.3)

#bin mode 
bin_mode(4,.3)

#bin mean
bin_mean(4,.5)

#bin skewness
bin_skewness(4,.2)

#bin variance
bin_variance(3,.5)

#bin probability
bin_probability(4,5,.4)

#bin variance
binvar(4,.4)

#bin distribution
bindis(4,.2)
plot(bindis(4,.2))

#bin cumulative
bincum(6,.4)
plot(bincum(6,.4))
```

